### 2025-01-05 README.Rmd
Update README

@@

embedplyr won't help you train new embedding models, but it can load embeddings from a file or download them from online. This is especially useful for pretrained word embedding models like GloVe, word2vec, and fastText. Dozens of these models can be conveniently downloaded from online sources with `load_embeddings()`.

```{r, warning=FALSE, message=FALSE}
library(embedplyr)

glove_twitter_25d <- load_embeddings("glove.twitter.27B.25d")
```

@@

Whereas indexing a regular matrix by rownames gets slower as the number of rows increases, embedingplyr's hash table indexing means that token embeddings can be retrieved in milliseconds even from models with millions of rows.

@@

`embed_docs()` can also be used to generate other types of embeddings. For example, we can use the '[text](https://r-text.org)' package to generate embeddings using any model available from Huggingface transformers.

>>>>

```{r, message=FALSE, warning=FALSE}
library(embedplyr)
```

@@

embedplyr won't help you train new embedding models, but it can load embeddings from a file or download them from online. This is especially useful for pretrained word embedding models like GloVe, word2vec, and fastText. Hundreds of these models can be conveniently downloaded from online sources with `load_embeddings()`.

One particularly useful feature of `load_embeddings()` is the optional `words` parameter, which allows the user to specify a subset of words to load from the model. This allows users to work with large models, which are often too large to load into an interactive environment in their entirety. For example, a user may specify the set of unique tokens in their corpus of interest, and load only these from the model.

```{r, eval=FALSE, warning=FALSE, message=FALSE}
# load 25d GloVe model trained on Twitter
glove_twitter_25d <- load_embeddings("glove.twitter.27B.25d")

# load words from 300d model trained on Google Books English Fiction 1800-1810
eng.fiction.all_sgns.1800 <- load_embeddings(
	"eng.fiction.all_sgns.1800",
	words = c("word", "token", "lemma")
	)
```

@@

Whereas indexing a regular matrix by rownames gets slower as the number of rows increases, embedplyr's hash table indexing means that token embeddings can be retrieved in milliseconds even from models with millions of rows.

@@

`embed_docs()` can also be used to generate other types of embeddings. For example, we can use the '[text](https://r-text.org)' package to generate embeddings using any model available from Hugging Face Transformers.
